VFTS682: a confirmed dynamical ejection?

### 2018-05-09 VFTS682.tex
./aa.cls

To compare the astrometry of VFTS682 and derive its peculiar motion,
we then select data from the Gaia DR2 catalog for two regions: the
``surroundings'' of VFTS 682, and the ``R136 cluster''. The
surrounding region is defined by all the stars in a target of 10 arcminutes around
VFTS682 fulfilling the following criteria: we require a G-band
magnitude brighter than 17, to mimic the completeness threshold for
the VFTS survey, \texttt{visibility\_period} >= 5, and
\texttt{astrometric\_excess\_noise} <= 1. This selection yields
roughly 1330 stars, including the subset of stars which we consider to be
part of R136, discussed below. We further require  these stars to have finite proper
motion components and relative errors, reducing further the sample to
1323 stars. % A more strict sample selection for the surroundings can
% be found in \cite{lennon:18}.

>>>>

To compare the astrometry of VFTS682 and derive its peculiar motion,
we then select data from the Gaia DR2 catalog for two regions: the
``surroundings'' of VFTS 682, and the ``R136 cluster''. The
surrounding region is defined by all the stars in a target of 10 arcminutes around
VFTS682 fulfilling the following criteria: we require \texttt{visibility\_period} >= 5,
\texttt{astrometric\_excess\_noise} <= 1, the error on the proper
motion components to be smaller than 0.07\,$\mathrm{mas\ yr^{-1}}$,
and the proper motion components themselves to be smaller than
2\,$\mathrm{mas\ yr^{-1}}$ in absolute value. At the distance to the
LMC, $1\mathrm{mas\ yr^{-1}}\simeq250\,\kms$, so the cut on the values
of the proper motions removes stars that would have projected
tangential velocities in excess of $\sim$500\,$\kms$, which are most
likely to be foreground stars \todo{clean phrasing here}.
This selection yields 182 stars.% , including the subset of stars which we consider to be
% part of R136, discussed below. We further require  these stars to have finite proper
% motion components and relative errors, reducing further the sample to
% 1323 stars.
% A more strict sample selection for the surroundings can
% be found in \cite{lennon:18}.
